A state space model reveals the rich and varied dynamics of hippocampal replay

### 2020-07-21 Article.tex
Update on Overleaf.

\subsection*{Replay distance from animal}
Replay distance from the animal is defined as the shortest path distance along the track graph between the animal's 2D position projected on to the track graph (see Linearization) and the MAP estimate of the posterior probability of position $\argmax_{x_k} p(x_{k} \mid O_{1:T})$, which is defined as the center of the position bin with the greatest posterior value. The shortest path is found using Dijkstra's algorithm.

@@

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification}.
Both code bases rely on the python packages: Numpy \cite{vanderWaltNumPyArrayStructure2011}, Numba \cite{LamNumbaLLVMbasedPython2015}, Matplotlib \cite{HunterMatplotlib2DGraphics2007}, xarray \cite{HoyerxarrayNDlabeled2017}, NetworkX \cite{HagbergExploringNetworkStructure2008}, Pandas \cite{McKinneyDataStructuresStatistical2010} and Seaborn (doi: 10.5281/zenodo.883859). All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.

>>>>

\subsection*{Replay distance from animal}
Replay distance from the animal is defined as the shortest path distance along the track graph between the animal's 2D position projected on to the track graph (see Linearization) and the MAP estimate of the posterior probability of position $\argmax_{x_k} p(x_{k} \mid O_{1:T})$, which is defined as the center of the position bin with the greatest posterior value. The shortest path is found using Dijkstra's algorithm \cite{Dijkstranotetwoproblems1959}.

@@

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification}.
Both code bases rely on the following python packages: Numpy \cite{vanderWaltNumPyArrayStructure2011}, Numba \cite{LamNumbaLLVMbasedPython2015}, Matplotlib \cite{HunterMatplotlib2DGraphics2007}, xarray \cite{HoyerxarrayNDlabeled2017}, NetworkX \cite{HagbergExploringNetworkStructure2008}, Pandas \cite{McKinneyDataStructuresStatistical2010} and Seaborn (doi: 10.5281/zenodo.883859). All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.
